---
title: ""
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r}
library(tidyverse)
library(leaflet)
library(ggplot2)
library(plotly)
library(readxl)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


Read in wine data.


```{r}
wine_df = 
  read_csv(
  "./wine_data/tidy/wine_all.csv")

### remove region 2, taster twitter and missing values in region 1.

#wine_type <- read_csv("./wine_data/winemag-data-130k-v2.csv") %>% 
#            group_by(variety) %>% 
#            count() %>% 
#            arrange(desc(n)) %>% 
#            as.tibble()

```


Make a plot of distribution of price/rating by type
```{r}

wine_df %>% 
  filter(!is.na(type),
         price <= 200) %>% 
  ggplot(aes(x = type, y = price, color = type)) +
  geom_violin()


wine_df %>% 
  filter(!is.na(type)) %>% 
  rename(rating = points) %>% 
  ggplot(aes(x = type, y = rating, color = type)) +
  geom_violin()



```

Make a plot of distribution of price/rating by region
```{r}
y <- list(
  title = "Mean Price"
)
wine_df %>% 
  filter(!is.na(price)) %>% 
  group_by(country) %>% 
  summarise(mean = mean(price)) %>% 
  mutate(country = fct_reorder(country, mean),
         mean = round(mean, 2),
        text_label=str_c("Country:", country, "\nmean price:", mean)) %>% 
  plot_ly(
  x = ~country, y = ~mean, color = ~country, text = ~text_label, 
  type = "bar", colors = "viridis") %>% 
  layout(yaxis = y)
  
  

y <- list(
  title = "Mean rating"
)
wine_df %>% 
  filter(!is.na(points)) %>% 
  group_by(country) %>% 
  summarise(mean = mean(points)) %>% 
  mutate(country = fct_reorder(country, mean),
         mean = round(mean, 2),
        text_label=str_c("Country:", country, "\nmean rating:", mean)) %>% 
  plot_ly(
  x = ~country, y = ~mean, color = ~country, text = ~text_label, 
  type = "bar", colors = "viridis") %>% 
  layout(yaxis = y)





```
Even though Switzerland has the highest priced wine, the average ratings is only ranked at 11. 




Make plots of ratings/price by year by wine type. 
```{r}


wine_df %>% 
  filter(!is.na(points),
         !is.na(type),
         year > 2000) %>% 
  group_by(year,type) %>% 
  summarise(mean = mean(points)) %>% 
  mutate(mean = round(mean, 2)) %>% 
  ggplot(aes(x = year, y = mean, color = type))+
  geom_point()+
  geom_line() +
  labs(y = "Mean rating",
      x = "Year",
      title = "change in mean ratings by wine type in 21 century")




wine_df %>% 
  filter(!is.na(price),
         !is.na(type),
         year > 2000) %>% 
  group_by(year,type) %>% 
  summarise(mean = mean(price)) %>% 
  mutate(mean = round(mean, 2)) %>% 
  ggplot(aes(x = year, y = mean, color = type))+
  geom_point()+
  geom_line() +
  labs(y = "Mean price",
      x = "Year",
      title = "change in mean price by wine type in 21 century")
```


Make plots of ratings by taster.
```{r}

y <- list(
  title = "Mean ratings"
)

  wine_df %>% 
  filter(!is.na(points)) %>% 
  group_by(taster_name) %>% 
  summarise(mean = mean(points)) %>% 
  mutate(taster_name = fct_reorder(taster_name, mean),
         mean = round(mean, 2),
        text_label=str_c("Taster:", taster_name, "\nmean rating:", mean)) %>% 
  plot_ly(
  x = ~taster_name, y = ~mean, color = ~taster_name, text = ~text_label, 
  type = "bar", colors = "viridis") %>% 
  layout(yaxis = y) 





```


who rates the highest price wine? (greater than $800)

```{r}

wine_df %>% 
  filter(price >= 800,
         !is.na(taster_name)) %>% 
  group_by(taster_name) %>% 
  count()


```
Most of the most expensive wine are rated by Roger Voss.



```{r}
wine_df %>% 
  filter(!is.na(taster_name)) %>% 
  group_by(taster_name) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  knitr::kable()

```

Roger Voss rates most number of wine at WineEthusiast Magazine. 


Get the winery which has the top average ratings wine. 

```{r}

wine_df %>% 
  filter(!is.na(winery)) %>% 
  group_by(winery,country) %>% 
  summarise(mean = mean(points)) %>% 
  arrange(desc(mean)) %>% 
  top_n(10)


```

